Supplemental Online Materials:\\\textit{Meta-Analysis of the `Ironic' Effects of Intergroup Contact}

### 2021-06-07 manuscript/supplemental-materials.tex
add starred references

As preregistered, we conducted two kinds of robustness checks. First, we
assessed to what extent our findings were sensitive to choosing
narrower, \(\mu \sim \text{Normal}(0, 0.1)\), or wider,
\(\mu \sim \text{Normal}(0, 1)\), prior distributions. Choosing narrower
or wider prior distribution did not affect mean effect size estimates
for perceived injustice (\(\Delta r = -.00, [-.05, .04]\) and
\(\Delta r = .00, [-.05, .05]\)), collective action
(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = .00, [-.11, .10]\)),
and policy support (\(\Delta r = -.01, [-.10, .08]\) and
\(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
findings were sensitive to including or excluding influential studies by
repeating the preregistered analyses \(J\) times while leaving out one
of \(J\) studies each time and by calculating the mean absolute
difference (\emph{MAD}) for the estimated mean effect size across
left-out studies. For perceived injustice
(\(\textit{MAD} = .02, [.01, .04]\)), collective action
(\(\textit{MAD} = .04, [.02, .09]\)), and policy support
(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
out the most influential study, for example, did not change estimates of
the mean effect size for the three outcomes
(\(\Delta r = .01, [-.04, .05]\); \(\Delta r = .02, [-.08, .12]\);
\(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that
our findings were robust to choosing different prior distributions and
to excluding influential studies.

>>>>

As preregistered, we conducted two kinds of robustness checks. First, we
assessed to what extent our findings were sensitive to choosing
narrower, \(\mu \sim \text{Normal}(0, 0.1)\), or wider,
\(\mu \sim \text{Normal}(0, 1)\), prior distributions. Choosing narrower
or wider prior distribution did not affect mean effect size estimates
for perceived injustice (\(\Delta r = -.00, [-.05, .04]\) and
\(\Delta r = .00, [-.05, .05]\)), collective action
(\(\Delta r = -.01, [-.11, .09]\) and \(\Delta r = .00, [-.11, .10]\)),
and policy support (\(\Delta r = -.01, [-.10, .08]\) and
\(\Delta r = .00, [-.09, .10]\)). Second, we assessed to what extent our
findings were sensitive to including or excluding influential studies by
repeating the preregistered analyses \(J\) times while leaving out one
of \(J\) studies each time and by calculating the mean absolute
difference (\emph{MAD}) for the estimated mean effect size across
left-out studies. For perceived injustice
(\(\textit{MAD} = .02, [.01, .04]\)), collective action
(\(\textit{MAD} = .04, [.02, .09]\)), and policy support
(\(\textit{MAD} = .03, [.02, .08]\)), the \emph{MAD} was small. Leaving
out the most influential study, for example, did not change estimates of
the mean effect size for the three outcomes
(\(\Delta r = -.00, [-.05, .04]\); \(\Delta r = .02, [-.08, .12]\);
\(\Delta r = -.02, [-.11, .07]\)). Together, these analyses showed that
our findings were robust to choosing different prior distributions and
to excluding influential studies.
